NLIZE: A Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models

### 2018-03-28 paper/application.tex
add figure

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{predictStability}
 \caption{
Prediction stability assessment. Isolate unstable one
 }
\label{fig:pipelineView}
\end{figure}

@@

\subsection{Scenario 1: Interpreting Decision Making Process}
Understand how the model arrive at the prediction is the first step  only essential for evaluating the model performance but also necessary for hypothesizing improvement strategies.
%
The three stages (encoder, attention, classifier) of the model work in synergy to produce the correct prediction.
%
%One of the essential task for can be made in either of these stages.
% \shusen{difference in sensitivity among entail natural and contradict relationships}
% the generate the correct prediction for the wrong reason

>>>>

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{predictStability}
 \caption{
Prediction stability assessment. Isolate unstable one
 }
\label{fig:predictStability}
\end{figure}

@@

\subsection{Scenario 1: Examine the Decision Making Process}
\begin{itemize}
\item if the prediction look for attention alignment
\item 
\end{itemize}

Understand how the model arrive at the prediction is the first step  only essential for evaluating the model performance but also necessary for hypothesizing improvement strategies.
%
The three stages (encoder, attention, classifier) of the model work in synergy to produce the correct prediction.

\begin{figure*}[t]
\centering
\vspace{-2mm}
 \includegraphics[width=0.9\linewidth]{failledEncoding}
 \caption{
The prediction is failed due to incorrect alignment. For all the failed case, 
 }
\label{fig:failedEncoding}
\end{figure*}

%One of the essential task for can be made in either of these stages.
% \shusen{difference in sensitivity among entail natural and contradict relationships}
% the generate the correct prediction for the wrong reason

Another
Does the model arrived at the correct prediction for the wrong reason?
